---
title: "Wrangle phylogeny prior to PGLS analyses"
output: html_document
---

Load libraries
```{r, message = FALSE, warning = FALSE}
library(ape)
library(geiger)
library(tidyverse)
library(phytools)
library(here)
```

Read in data and phylogeny
```{r, message = FALSE, warning = FALSE}
max_bf <- read_csv(here("data/max_bf.csv"))
lepidosaurtree <- read.tree(here("raw-data/WrightTree.nex"))
str(lepidosaurtree)
```

Replace spaces with underscores (_) so they match up with species names in the tree
```{r}
max_bf <-
  max_bf %>%
  mutate(tips = str_replace(BinomialReptileDatabase, " ", "_"))
```

Update taxonomy in tree to match Uetz 2020.
```{r}
lepidosaurtree$tip.label <- gsub("Typhlosaurus_lineatus", "Acontias_kgalagadi",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Glaphyromorphus_isolepis", "Eremiascincus_isolepis",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Cordylus_cataphractus", "Ouroborus_cataphractus",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Cordylus_warreni", "Smaug_mossambicus",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Uromastyx_acanthinura", "Uromastix_acanthinura",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Microacontias_litoralis", "Acontias_litoralis",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Cryptoblepharus_boutonii",
                                 "Cryptoblepharus_metallicus", lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Gallotia_gomerana", "Gallotia_bravoana",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Liolaemus_zullyi", "Liolaemus_zullyae",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Podarcis_atrata", "Podarcis_liolepis",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Laudakia_stellio", "Stellagama_stellio",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Bradypodion_caffrum", "Bradypodion_caffer",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Cordylus_polyzonus", "Karusasaurus_polyzonus",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Lygosoma_afrum", "Mochlus_sundevallii",
                                 lepidosaurtree$tip.label)
lepidosaurtree$tip.label <- gsub("Tupinambis_merianae", "Salvator_merianae",
                                 lepidosaurtree$tip.label)
```

Add species that are missing from the phylogeny, based on other phylogenies in the literature. Create separate tree so we can use trees without added species if needed.
```{r}
lepidosaurtree2 <- lepidosaurtree

lepidosaurtree2 <- bind.tip(lepidosaurtree2, tip.label = "Bradypodion_kentanicum",
                           where = 2446, position = 0.1)
lepidosaurtree2 <- bind.tip(lepidosaurtree2, tip.label = "Liolaemus_mapuche",
                           where = 2768, position = 0.1)
lepidosaurtree2 <- bind.tip(lepidosaurtree2, tip.label = "Bradypodion_caeruleogula",
                           where = 6618, position = 0.5)
lepidosaurtree2 <- bind.tip(lepidosaurtree2, tip.label = "Xenosaurus_newmanorum",
                           where = 3341, position = 0.1)
lepidosaurtree2 <- bind.tip(lepidosaurtree2, tip.label = "Anolis_pentaprion",
                           where = 2970, position = 0.1)
```

Identify mismatches between species in the data and phylogenies
```{r}
check <- name.check(phy = lepidosaurtree, 
                    data = max_bf, data.names = max_bf$tips)
check2 <- name.check(phy = lepidosaurtree2, 
                    data = max_bf, data.names = max_bf$tips)
```

Drop species missing from the trees which are not in our data using drop.tip
```{r}
lepidosaurtree <- drop.tip(lepidosaurtree, check$tree_not_data)
lepidosaurtree2 <- drop.tip(lepidosaurtree2, check$tree_not_data)
```

Check various tree properties (should all be TRUE)
```{r}
is.binary.tree(lepidosaurtree)
is.ultrametric(lepidosaurtree)
is.rooted(lepidosaurtree)
is.binary.tree(lepidosaurtree2)
is.ultrametric(lepidosaurtree2)
is.rooted(lepidosaurtree2)
```

Save trees for future use
```{r}
write.nexus(lepidosaurtree, file = here("data/lepidosaur-tree.nex"))
write.nexus(lepidosaurtree2, file = here("data/lepidosaur-tree-plus.nex"))
```
                                