---
title: "Exploring the data: distribution across taxonomy/phylogeny"
author: "Natalie Cooper"
---


Load libraries
```{r}
library(ape)
library(tidyverse)
library(geiger)
library(tidytree)
library(treeio)
library(ggtree)
library(knitr)
library(ggstance)
library(patchwork)

# Helper functions for plotting
remove_y <- 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

remove_x <- 
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

# Colour palette
sf_colours <- c("#ffc100", "#47b881", "brown", "#5588ff", 
                "#efbbff", "#ff7400", "#090088", "#800080")

# "Acrodonta"    #ffc100 = yellow   
# "Anguimorpha"     #47b881 = green
# "Dibamia"     "brown"    
# "Gekkota" #5588ff = lighter blue       
# "Lacertoidea"    #efbbff = pink
# "Pleurodonta"     #ff7400 = orange
# "Rhynchocephalia" #090088 = dark blue
# "Scincoidea" #800080 = purple

```

Read in the tree and the data, including the bite force data and the summary taxonomy data from Uetz et al 2020 plus higher taxonomy from Burbrink et al 2019.

```{r}
tree <- read.nexus(here("data/family-tree.nex"))
ds <- read_csv(here("data/max_bf.csv"))
taxa <- read_csv(here("data/taxonomy-data.csv"))
```

First let's look at the numbers per family, and how the % coverage looks for each family relative to the studies and to the taxonomic distributions...

```{r}
family_ds <-
  ds %>%
  group_by(Family) %>%
  summarise(nBF = n()) %>%
  full_join(taxa) %>%
  mutate(percent_taxa = (nBF/Species_Uetz) * 100) %>%
  mutate(percent_studies = (nBF/164) * 100) %>%
  select(HigherTaxonomy, everything()) %>%
  arrange(HigherTaxonomy, Family)

# Replace NAs with 0
family_ds[is.na(family_ds)] <- 0

# Print
kable(family_ds, digits = 3)
```

Next let's look at the numbers per higher taxonomic group, and how the % coverage looks for each family relative to the studies and to the taxonomic distributions...

```{r}
# Summarise the taxonomy data so it gives numbers per superfamily not family
taxa_higher <-
  taxa %>%
  group_by(HigherTaxonomy) %>%
  summarise(species_Uetz = sum(Species_Uetz))

higher_ds <-
  ds %>%
  group_by(HigherTaxonomy) %>%
  summarise(nBF = n()) %>%
  full_join(taxa_higher) %>%
  mutate(percent_taxa = (nBF/species_Uetz) * 100) %>%
  mutate(percent_studies = (nBF/164) * 100) %>%
  arrange(HigherTaxonomy)
  
# Replace NAs with 0
higher_ds[is.na(higher_ds)] <- 0

# Print
kable(higher_ds, digits = 3)
```

### Plots of distributions

Family level plots
```{r}
p1 <- 
  ggplot(family_ds, aes(y = nBF, x = Family, fill = HigherTaxonomy)) + 
  geom_bar(position = position_stack(reverse = TRUE), stat = "identity") +
  scale_fill_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  #scale_y_continuous(breaks=seq(0,45,5)) +
  xlab("Family") +
  ylab("species (n)") +
  theme(legend.position = "none")

# To aid plotting switch 100 for 0 in Sphenodon
family_ds[family_ds == 100] <- 0

p2 <-
  ggplot(family_ds, aes(y = percent_taxa, x = Family, fill = HigherTaxonomy)) + 
  geom_bar(position = position_stack(reverse = TRUE), stat = "identity") +
  scale_fill_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  #scale_y_continuous(breaks=seq(0,50,5)) +
  xlab("Family") +
  ylab("coverage (%)") +
  theme(legend.position = "right") +
  remove_y

p1 + p2

# Save plot
#ggsave(here("figures/family-level-data-coverage.png"), height = 7)
```

Higher taxonomy level plots
```{r}
p1 <- 
  ggplot(higher_ds, aes(y = nBF, x = HigherTaxonomy, fill = HigherTaxonomy)) + 
  geom_bar(position = position_stack(reverse = TRUE), stat = "identity") +
  scale_fill_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  ylim(0, 80) +
  #scale_y_continuous(breaks=seq(0,45,5)) +
  xlab("Taxonomic group") +
  ylab("species (n)") +
  theme(legend.position = "none")

# To aid plotting switch 100 for 0 in Sphenodon
higher_ds[higher_ds == 100] <- 0

p2 <-
  ggplot(higher_ds, aes(y = percent_taxa, x = HigherTaxonomy, fill = HigherTaxonomy)) + 
  geom_bar(position = position_stack(reverse = TRUE), stat = "identity") +
  scale_fill_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  ylim(0,10) +
  xlab("Taxonomic group") +
  ylab("coverage (%)") +
  theme(legend.position = "none") +
  remove_y

p1 + p2

# Save plot
# ggsave(here("figures/higher-level-data-coverage.png"), height = 5)

```

### Plotting on the phylogeny

Ensure the data is in the same order as the tree and make it into a dataframe
```{r}
family_ds <- family_ds[match(tree$tip.label, family_ds$Family),]

# Replace 0s with NA
family_ds[is.na(family_ds)] <- 0

# Reorder the columns so Family is first
family_ds <-
  family_ds %>%
  select(Family, everything())

# Add rownames as family names
rownames(family_ds) <- family_ds$Family

# Make sure family_ds is a dataframe
family_ds <- as.data.frame(family_ds)
```

Make trees using ggtree.

Note that this code will throw lots of warnings about scales which can be ignored
```{r}
tree_cols <- c("brown", rep("#5588ff", 7), rep("#efbbff", 10),
               rep("#ffc100", 2), rep("#ff7400", 12), rep("#47b881", 7),
               rep("#800080", 4), "#090088")

# Make the tree base
base <- 
  ggtree(tree) +
  geom_tiplab(geom = "text", offset = 5, col = tree_cols)

# Plot species numbers as facet
p1 <- facet_plot(base, panel = 'Species (n)', 
                data = family_ds, 
                geom = geom_barh, 
                mapping = aes(x = nBF,
                              fill = HigherTaxonomy), 
                stat = 'identity') +
  theme(legend.position = "none") +
  scale_fill_manual(values = sf_colours)

# Plot % coverage as facet on top of old facet
p2 <- 
  facet_plot(p1, panel = 'Coverage (%)', 
                data = family_ds, 
                geom = geom_barh, 
                mapping = aes(x = percent_taxa,
                              fill = HigherTaxonomy), 
                stat = 'identity') +
  theme_bw(base_size = 14) + 
  theme(legend.position = "right", legend.title = element_blank(),
        strip.background = element_rect(fill="white")) +
  xlim_tree(500) + 
  xlim_expand(c(0, 5), 'Coverage (%)') +
  remove_y +
  scale_fill_manual(values = sf_colours)

p2

# Save the plot
#ggsave(here("figures/phylogeny-data-coverage-colours.png"), height = 7, width = 10)


#### NOT INCLUDED BUT LEFT HERE FOR REFERENCE

# Creat new mini dataset to add the x labels
#d <- data.frame(.panel = c('Tree', 'Species in dataset (n)', 'Taxonomic coverage (%)'), 
#                lab = c("time (MYA)", "number", "%"), 
#                x = c(250, 20, 50), y = -2)

# Add x labels
#p2 + scale_y_continuous(limits = c(0, 45), 
                        #expand = c(0,0), 
                        #oob = function(x, ...) x) +
    #geom_text(aes(label = lab), data=d) + 
    #coord_cartesian(clip = 'off')  + 
    #theme(plot.margin = margin(6, 6, 40, 6))

```


```{r}
# To make a tree with tip labels coloured by group
# note that you cannot put this into a facet plot
base %<+% family_ds + geom_tippoint(aes(color = HigherTaxonomy), size = 3) +
  scale_colour_manual(values = sf_colours)

# To make a tree with branches coloured by group
# note that you cannot put this into a facet plot
circ <- 
  ggtree(tree, layout = "circular") +
  geom_tiplab(geom = "text", offset = 5)

# Add colours based on HigherTaxonomy
grp <- list(Acrodonta = c(family_ds$Family[family_ds$HigherTaxonomy == "Acrodonta"]), 
            Anguimorpha = c(family_ds$Family[family_ds$HigherTaxonomy == "Anguimorpha"]), 
            Dibamia = c(family_ds$Family[family_ds$HigherTaxonomy == "Dibamia"]), 
            Gekkota = c(family_ds$Family[family_ds$HigherTaxonomy == "Gekkota"]), 
            Lacertoidea = c(family_ds$Family[family_ds$HigherTaxonomy == "Lacertoidea"]), 
            Pleurodonta = c(family_ds$Family[family_ds$HigherTaxonomy == "Pleurodonta"]), 
            Rhynchocephalia = c(family_ds$Family[family_ds$HigherTaxonomy == "Rhynchocephalia"]),
            Scincoidea = c(family_ds$Family[family_ds$HigherTaxonomy == "Scincoidea"])) 

  groupOTU(circ, grp, 'HigherTaxonomy') + aes(color = HigherTaxonomy) +
  scale_colour_manual(values = c("black", sf_colours)) +
  theme(legend.position="none")
  
# Save tree plot
# Currently doesn't fit all tip labels in plot window...
# ggsave(here("figures/phylogeny-family-coloured.png"), height = 10, width = 30)
```

