---
title: "Exploring the data: distribution of biteforce"
author: "Natalie Cooper"
---

Load libraries
```{r}
library(ape)
library(tidyverse)
library(geiger)
#library(tidytree)
library(treeio)
library(ggtree)
#library(knitr)
library(ggstance)
library(patchwork)
library(here)

# Helper functions for plotting
remove_y <- 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

remove_x <- 
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

# Colour palette
sf_colours <- c("#ffc100", "#47b881", "#5588ff", 
                "#efbbff", "#ff7400", "#090088", "#800080")

# "Acrodonta"    #ffc100 = yellow   
# "Anguimorpha"     #47b881 = green
# "Dibamia"     "brown"    
# "Gekkota" #5588ff = lighter blue       
# "Lacertoidea"    #efbbff = pink
# "Pleurodonta"     #ff7400 = orange
# "Rhynchocephalia" #090088 = dark blue
# "Scincoidea" #800080 = purple
```

Read in the data
```{r, message = FALSE}
ds1 <- read_csv(here("data/max_bf.csv"))
ds1_male <- read_csv(here("data/max_bf_males.csv"))
ds1_female <- read_csv(here("data/max_bf_females.csv"))

## Remove the species not in the tree and therefore not in the analyses
ds1 <-
  ds1 %>%
  filter(BinomialReptileDatabase != "Diplolaemus leopardinus" &
          BinomialReptileDatabase != "Tropidurus semitaeniatus" &
           BinomialReptileDatabase != "Aspidoscelis sonorae")

ds1_male <-
  ds1_male %>%
  filter(BinomialReptileDatabase != "Diplolaemus leopardinus" &
          BinomialReptileDatabase != "Tropidurus semitaeniatus" &
           BinomialReptileDatabase != "Aspidoscelis sonorae")

ds1_female <-
  ds1_female %>%
  filter(BinomialReptileDatabase != "Diplolaemus leopardinus" &
          BinomialReptileDatabase != "Tropidurus semitaeniatus" &
           BinomialReptileDatabase != "Aspidoscelis sonorae")


# Stick the datasets together
both1 <- rbind(ds1_female, ds1_male)

# And for all the data
ds1a <-
  ds1 %>%
  mutate(Sex = rep("Both", length(ds1$Sex)))

all <- rbind(both1, ds1a)
```


First, what's the range of body sizes and BF?

```{r}
all %>%
  summarise(min(max_svl), max(max_svl),
            min(max_bf), max(max_bf))
```


Now let's look at bite force per family
```{r}
family_bf1 <-
  ds1 %>%
  group_by(Family, HigherTaxonomy) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

family_bf1

#write_csv(family_bf1, path = here("tables/bite-force-by-family.csv"))
```

```{r}
ggplot(ds1, aes(y = log(max_bf), x = Family, colour = HigherTaxonomy)) + 
  geom_point(alpha = 0.5) +
  geom_point(data = family_bf1, aes(y = MeanBF), size = 3) +
  geom_errorbar(data = family_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.4) +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  #scale_y_continuous(breaks=seq(0,45,5)) +
  xlab("Family") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank())

# Save plot
#ggsave(here("figures/bite-force-by-family.png"), height = 5)
```

Bite force per higher grouping
```{r}
higher_bf1 <-
  ds1 %>%
  group_by(HigherTaxonomy) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

higher_bf1

#write_csv(higher_bf1, path = here("tables/bite-force-by-higher.csv"))
```

```{r}
ggplot(ds1, aes(y = log(max_bf), x = HigherTaxonomy, colour = HigherTaxonomy)) + 
  geom_point(alpha = 0.5) +
  geom_point(data = higher_bf1, aes(y = MeanBF), size = 3) +
  geom_errorbar(data = higher_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2) +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("Family") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank())

# Save plot
#ggsave(here("figures/bite-force-by-higher.png"), height = 5, width = 7)
```

Bite force per higher grouping
```{r}
higher_bf1 <-
  ds1 %>%
  group_by(HigherTaxonomy) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

higher_bf1

#write_csv(higher_bf1, path = here("tables/bite-force-by-higher.csv"))
```

```{r}
higherplot <-
  ggplot(ds1, aes(y = log(max_bf), x = HigherTaxonomy, colour = HigherTaxonomy)) + 
  geom_jitter(alpha = 0.5, width = 0.2) +
  geom_point(data = higher_bf1, aes(y = MeanBF), size = 3) +
  geom_errorbar(data = higher_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2) +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "none", legend.title = element_blank()) +
  labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))

# Save plot
#ggsave(here("figures/bite-force-by-higher.png"), height = 5, width = 7)
```

Bite force per diet
```{r}
diet_bf1 <-
  ds1 %>%
  filter(!is.na(Diet)) %>%
  group_by(Diet) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

diet_bf1

#write_csv(diet_bf1, path = here("tables/bite-force-by-diet.csv"))
```

```{r}
# Remove NAs
ds1_diet <- filter(ds1, !is.na(Diet))

dietplot <-
  ggplot(ds1_diet, aes(y = log(max_bf), x = Diet)) + 
  geom_jitter(alpha = 0.5, width = 0.2) +
  geom_point(data = diet_bf1, aes(y = MeanBF), size = 3, col = "#880F0A") +
  geom_errorbar(data = diet_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2, col = "#880F0A") +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))
```

Bite force per arboreality
```{r}
arb_bf1 <-
  ds1 %>%
  filter(!is.na(arboreal)) %>%
  group_by(arboreal) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

arb_bf1

#write_csv(arb_bf1, path = here("tables/bite-force-by-arboreal.csv"))
```

```{r}
# Remove NAs
ds1_arb <- filter(ds1, !is.na(arboreal))

arbplot <-
  ggplot(ds1_arb, aes(y = log(max_bf), x = arboreal)) + 
  geom_jitter(alpha = 0.5, width = 0.2) +
  geom_point(data = arb_bf1, aes(y = MeanBF), size = 3, col = "#880F0A") +
  geom_errorbar(data = arb_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2, col = "#880F0A") +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "E") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))
```

Bite force per fossoriality
```{r}
fos_bf1 <-
  ds1 %>%
  filter(!is.na(fossorial)) %>%
  group_by(fossorial) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

fos_bf1

#write_csv(fos_bf1, path = here("tables/bite-force-by-fossorial.csv"))
```

```{r}
# Remove NAs
ds1_fos <- filter(ds1, !is.na(fossorial))

fosplot <-
  ggplot(ds1_fos, aes(y = log(max_bf), x = fossorial)) + 
  geom_jitter(alpha = 0.5, width = 0.2) +
  geom_point(data = fos_bf1, aes(y = MeanBF), size = 3, col = "#880F0A") +
  geom_errorbar(data = fos_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2, col = "#880F0A") +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))
```

Bite force per saxicolous
```{r}
sax_bf1 <-
  ds1 %>%
  # Relevel
  mutate(saxicolous = relevel(as.factor(saxicolous), ref = "Saxicolous")) %>%
  filter(!is.na(saxicolous)) %>%
  group_by(saxicolous) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

sax_bf1

#write_csv(sax_bf1, path = here("tables/bite-force-by-saxicolous.csv"))
```

```{r}
# Remove NAs
ds1_sax <- 
  ds1 %>%
  # Relevel
  mutate(saxicolous = relevel(as.factor(saxicolous), ref = "Saxicolous")) %>%
  filter(!is.na(saxicolous))

saxplot <-
  ggplot(ds1_sax, aes(y = log(max_bf), x = saxicolous)) + 
  geom_jitter(alpha = 0.5, width = 0.2) +
  geom_point(data = sax_bf1, aes(y = MeanBF), size = 3, col = "#880F0A") +
  geom_errorbar(data = sax_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2, col = "#880F0A") +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "F") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))
```

Bite force by tooth attachment
```{r}
acrodont_bf1 <-
  ds1 %>%
  filter(!is.na(acrodont)) %>%
  group_by(acrodont) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

acrodont_bf1

#write_csv(acrodont_bf1, path = here("tables/bite-force-by-acrodont.csv"))
```

```{r}
#
ds1_acrodont <- filter(ds1, !is.na(acrodont))

acrodontplot <-
  ggplot(ds1_acrodont, aes(y = log(max_bf), x = acrodont)) + 
  geom_jitter(alpha = 0.5, width = 0.2) +
  geom_point(data = acrodont_bf1, aes(y = MeanBF), size = 3, col = "#880F0A") +
  geom_errorbar(data = acrodont_bf1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2, col = "#880F0A") +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))
```

```{r}
# Plot all together
higherplot + acrodontplot + dietplot + fosplot + arbplot + saxplot +
  plot_layout(widths = c(2, 2), ncol = 2)

# Save plot
#ggsave(here("figures/bite-force-by-ecology.png"), height = 7)
```



## Males and females

```{r}
family_both1 <-
  both1 %>%
  group_by(Sex, Family, HigherTaxonomy) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

family_both1 

#write_csv(family_both1, path = here("tables/bite-force-by-family-sex.csv"))
```

```{r}
ggplot(both1, aes(y = log(max_bf), x = Family, colour = HigherTaxonomy)) + 
  geom_point(alpha = 0.5) +
  geom_point(data = family_both1, aes(y = MeanBF), size = 3) +
  geom_errorbar(data = family_both1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.4) +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  #scale_y_continuous(breaks=seq(0,45,5)) +
  xlab("Family") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank(),
        strip.background = element_rect(fill="white")) +
  facet_wrap(~Sex, ncol = 1)

# Save plot
#ggsave(here("figures/bite-force-by-family-sex.png"), height = 6)
```

Bite force per higher grouping
```{r}
higher_both1 <-
  both1 %>%
  group_by(Sex, HigherTaxonomy) %>%
  summarise(MeanBF = round(mean(log(max_bf)), digits = 3),
            SeBF = round(sd(log(max_bf))/sqrt(n()), digits = 3),
            n())

higher_both1

#write_csv(higher_both1, path = here("tables/bite-force-by-higher-sex.csv"))
```

```{r}
ggplot(both1, aes(y = log(max_bf), x = HigherTaxonomy, colour = HigherTaxonomy)) + 
  geom_point(alpha = 0.5) +
  geom_point(data = higher_both1, aes(y = MeanBF), size = 3) +
  geom_errorbar(data = higher_both1, 
                aes(y = MeanBF, ymin = MeanBF - SeBF, ymax = MeanBF + SeBF), 
                show.legend = FALSE, width = 0.2) +
  scale_colour_manual(values = sf_colours) +
  coord_flip() +
  theme_bw(base_size = 14) +
  xlab("Family") +
  ylab("ln(bite-force) (N)") + 
  ylim(-3, 7) +
  theme(legend.position = "right", legend.title = element_blank(),
        strip.background = element_rect(fill="white")) +
  facet_wrap(~Sex, ncol = 1)

# Save plot
#ggsave(here("figures/bite-force-by-higher-sex.png"), height = 5)
```

## Density plots

```{r}
bf <-  
  ggplot(all, aes(x=log(max_bf), colour = Sex)) +
  geom_density() +
  theme_bw(base_size = 14) +
  xlab("ln(bite-force) (N)") +
  scale_colour_manual(values = c("black", "orange1", "seagreen")) +
  theme(legend.position = "top") +
  xlim(-2.5,6) +
  annotate(geom = "text", x = 5.5, y = 0.3, label = "n = 161", size = 4) +
  annotate(geom = "text", x = 5.5, y = 0.25, label = "n = 112", size = 4, colour = "orange1") +
  annotate(geom = "text", x = 5.5, y = 0.2, label = "n = 132", size = 4, colour = "seagreen") +
      labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))

svl <-  
  ggplot(all, aes(x=log(max_svl), colour = Sex)) +
  geom_density() +
  theme_bw(base_size = 14) +
  xlab("ln(SVL) (mm)") +
  ylim(0, 1.5) +
  xlim(0, 6) +
  scale_colour_manual(values = c("black", "orange1", "seagreen")) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 5.2, y = 1.4, label = "n = 161", size = 4) +
  annotate(geom = "text", x = 5.2, y = 1.25, label = "n = 112", size = 4, colour = "orange1") +
  annotate(geom = "text", x = 5.2, y = 1.1, label = "n = 132", size = 4, colour = "seagreen") +
      labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))


hw <-  
  ggplot(all, aes(x=log(max_hw), colour = Sex)) +
  geom_density() +
  theme_bw(base_size = 14) +
  xlab("ln(head width) (mm)") +
  ylim(0, 1.5) +
  xlim(0, 6) +
  scale_colour_manual(values = c("black", "orange1", "seagreen")) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 5, y = 1.4, label = "n = 142", size = 4) +
  annotate(geom = "text", x = 5, y = 1.25, label = "n = 96  ", size = 4, colour = "orange1") +
  annotate(geom = "text", x = 5, y = 1.1, label = "n = 115", size = 4, colour = "seagreen") +
      labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))

hl <-  
  ggplot(all, aes(x=log(max_hl), colour = Sex)) +
  geom_density() +
  theme_bw(base_size = 14) +
  xlab("ln(head length) (mm)") +
  ylim(0, 1.5) +
  xlim(0, 6) +
  scale_colour_manual(values = c("black", "orange1", "seagreen")) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 5, y = 1.4, label = "n = 136", size = 4) +
  annotate(geom = "text", x = 5, y = 1.25, label = "n = 97  ", size = 4, colour = "orange1") +
  annotate(geom = "text", x = 5, y = 1.1, label = "n = 116", size = 4, colour = "seagreen") +
      labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))

hh <-  
  ggplot(all, aes(x=log(max_hh), colour = Sex)) +
  geom_density() +
  theme_bw(base_size = 14) +
  xlab("ln(head height) (mm)") +
  ylim(0, 1.5) +
  xlim(0, 6) +
  scale_colour_manual(values = c("black", "orange1", "seagreen")) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 5, y = 1.4, label = "n = 136", size = 4) +
  annotate(geom = "text", x = 5, y = 1.25, label = "n = 96  ", size = 4, colour = "orange1") +
  annotate(geom = "text", x = 5, y = 1.1, label = "n = 114", size = 4, colour = "seagreen") +
      labs(tag = "E") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))

bf / (svl + hw) / (hl + hh)

# Save the plot
# ggsave(here("figures/variable-density-plots-sex-all.png"), height = 8)
```