---
title: "Biteforce body size and ecology figures"
output: html_document
---

## Preparation

Load libraries
```{r}
library(ape)
library(tidyverse)
library(geiger)
library(tidytree)
library(treeio)
library(ggtree)
library(knitr)
library(caper)
library(ggstance)
library(patchwork)

# Helper functions for plotting
remove_y <- 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

remove_x <- 
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

# Colour palette
sf_colours <- c("#ffc100", "#47b881", "#5588ff", 
                "#efbbff", "#ff7400", "#090088", "#800080")

# "Acrodonta"    #ffc100 = yellow   
# "Anguimorpha"     #47b881 = green
# "Dibamia"     "brown"    
# "Gekkota" #5588ff = lighter blue       
# "Lacertoidea"    #efbbff = pink
# "Pleurodonta"     #ff7400 = orange
# "Rhynchocephalia" #090088 = dark blue
# "Scincoidea" #800080 = purple

# Diet
d_colours <- c("#56B4E9", "#009E73", "#D55E00")

# Diet
a_colours <- c("#00783e", "grey")

# Fossorial
f_colours <- c("#663300", "grey")
```

Read in the data and ensure these are dataframes.
```{r, message = FALSE}
max_bf <- read_csv(here("data/max_bf.csv"))
max_bf <- data.frame(max_bf)

max_bf_females <- read_csv(here("data/max_bf_females.csv"))
max_bf_females <- data.frame(max_bf_females)

max_bf_males <- read_csv(here("data/max_bf_males.csv"))
max_bf_males <- data.frame(max_bf_males)
```

Read in phylogeny
```{r}
tree <- read.nexus(here("data/lepidosaur-tree.nex"))
tree_plus <- read.nexus(here("data/lepidosaur-tree-plus.nex"))
```

Create comparative data objects with phylogeny and data combined
```{r}
lepidosaur <- comparative.data(phy = tree_plus, data = max_bf, 
                               names.col = tips, vcv = TRUE,
                               warn.dropped = FALSE, na.omit = FALSE)
# Females only
lepidosaur_females <- comparative.data(phy = tree_plus, data = max_bf_females, 
                               names.col = tips, vcv = TRUE,
                               warn.dropped = FALSE, na.omit = FALSE)
# Males only
lepidosaur_males <- comparative.data(phy = tree_plus, data = max_bf_males, 
                               names.col = tips, vcv = TRUE,
                               warn.dropped = FALSE, na.omit = FALSE)
```

Fit models to get regression lines
```{r}
# SVL
model1d <- pgls(log(max_bf) ~ log(max_svl)* as.factor(Diet), data = lepidosaur,
                   lambda = "ML")
model1a <- pgls(log(max_bf) ~ log(max_svl)* as.factor(arboreal), data = lepidosaur,
                   lambda = "ML", bounds = list(lambda = c(0.1,1)))
model1f <- pgls(log(max_bf) ~ log(max_svl) * as.factor(fossorial), data = lepidosaur,
                   lambda = "ML")

# HW
model2d <- pgls(log(max_bf) ~ log(max_hw)* as.factor(Diet), data = lepidosaur,
                   lambda = "ML")
model2a <- pgls(log(max_bf) ~ log(max_hw)* as.factor(arboreal), data = lepidosaur,
                   lambda = "ML")
model2f <- pgls(log(max_bf) ~ log(max_hw) * as.factor(fossorial), data = lepidosaur,
                   lambda = "ML")

# HL
model3d <- pgls(log(max_bf) ~ log(max_hl)* as.factor(Diet), data = lepidosaur,
                   lambda = "ML")
model3a <- pgls(log(max_bf) ~ log(max_hl)* as.factor(arboreal), data = lepidosaur,
                   lambda = "ML")
model3f <- pgls(log(max_bf) ~ log(max_hl) * as.factor(fossorial), data = lepidosaur,
                   lambda = "ML")

# HH
model4d <- pgls(log(max_bf) ~ log(max_hh)* as.factor(Diet), data = lepidosaur,
                   lambda = "ML")
model4a <- pgls(log(max_bf) ~ log(max_hh)* as.factor(arboreal), data = lepidosaur,
                   lambda = "ML")
model4f <- pgls(log(max_bf) ~ log(max_hh) * as.factor(fossorial), data = lepidosaur,
                   lambda = "ML")
```

Plots coloured by DIET

```{r}
# Remove NAs
lepidosaur_d <- filter(lepidosaur$data, !is.na(Diet))

svl <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_svl), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(SVL) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model1d)[1], 
              slope = coefficients(model1d)[2], colour = d_colours[1]) +
  geom_abline(intercept = coefficients(model1d)[1] + coefficients(model1d)[3], 
              slope = coefficients(model1d)[2] + coefficients(model1d)[5], colour = d_colours[2]) +
  geom_abline(intercept = coefficients(model1d)[1] + coefficients(model1d)[4], 
              slope = coefficients(model1d)[2] + coefficients(model1d)[6], colour = d_colours[3])

hw <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_hw), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head width) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model2d)[1], 
              slope = coefficients(model2d)[2], colour = d_colours[1]) +
  geom_abline(intercept = coefficients(model2d)[1] + coefficients(model2d)[3], 
              slope = coefficients(model2d)[2] + coefficients(model2d)[5], colour = d_colours[2]) +
  geom_abline(intercept = coefficients(model2d)[1] + coefficients(model2d)[4], 
              slope = coefficients(model2d)[2] + coefficients(model2d)[6], colour = d_colours[3])
  
hl <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_hl), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head length) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model3d)[1], 
              slope = coefficients(model3d)[2], colour = d_colours[1]) +
  geom_abline(intercept = coefficients(model3d)[1] + coefficients(model3d)[3], 
              slope = coefficients(model3d)[2] + coefficients(model3d)[5], colour = d_colours[2]) +
  geom_abline(intercept = coefficients(model3d)[1] + coefficients(model3d)[4], 
              slope = coefficients(model3d)[2] + coefficients(model3d)[6], colour = d_colours[3])
  
hh <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_hh), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head height) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))  +
  geom_abline(intercept = coefficients(model4d)[1], 
              slope = coefficients(model4d)[2], colour = d_colours[1]) +
  geom_abline(intercept = coefficients(model4d)[1] + coefficients(model4d)[3], 
              slope = coefficients(model4d)[2] + coefficients(model4d)[5], colour = d_colours[2]) +
  geom_abline(intercept = coefficients(model4d)[1] + coefficients(model4d)[4], 
              slope = coefficients(model4d)[2] + coefficients(model4d)[6], colour = d_colours[3])

(svl + hw) / (hl + hh)

# Save plot
#ggsave(here("figures/bodysize-bite-force-diet.png"), height = 5)
```

Plots coloured by ARBOREAL

```{r}
# Remove NAs
lepidosaur_a <- filter(lepidosaur$data, !is.na(arboreal))

svl <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_svl), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(SVL) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model1a)[1], 
              slope = coefficients(model1a)[2], colour = a_colours[1]) +
  geom_abline(intercept = coefficients(model1a)[1] + coefficients(model1a)[3], 
              slope = coefficients(model1a)[2] + coefficients(model1a)[4], colour = a_colours[2])

hw <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_hw), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head width) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model2a)[1], 
              slope = coefficients(model2a)[2], colour = a_colours[1]) +
  geom_abline(intercept = coefficients(model2a)[1] + coefficients(model2a)[3], 
              slope = coefficients(model2a)[2] + coefficients(model2a)[4], colour = a_colours[2])
  
hl <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_hl), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head length) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model3a)[1], 
              slope = coefficients(model3a)[2], colour = a_colours[1]) +
  geom_abline(intercept = coefficients(model3a)[1] + coefficients(model3a)[3], 
              slope = coefficients(model3a)[2] + coefficients(model3a)[4], colour = a_colours[2])
  
hh <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_hh), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head height) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))  +
  geom_abline(intercept = coefficients(model4a)[1], 
              slope = coefficients(model4a)[2], colour = a_colours[1]) +
  geom_abline(intercept = coefficients(model4a)[1] + coefficients(model4a)[3], 
              slope = coefficients(model4a)[2] + coefficients(model4a)[4], colour = a_colours[2])

(svl + hw) / (hl + hh)

# Save plot
#ggsave(here("figures/bodysize-bite-force-arboreal.png"), height = 5)
```

Plots coloured by ARBOREAL

```{r}
# Remove NAs
lepidosaur_f <- filter(lepidosaur$data, !is.na(fossorial))

svl <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_svl), colour = fossorial)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(SVL) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model1f)[1], 
              slope = coefficients(model1f)[2], colour = f_colours[1]) +
  geom_abline(intercept = coefficients(model1f)[1] + coefficients(model1f)[3], 
              slope = coefficients(model1f)[2] + coefficients(model1f)[4], colour = f_colours[2])

hw <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_hw), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head width) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model2f)[1], 
              slope = coefficients(model2f)[2], colour = f_colours[1]) +
  geom_abline(intercept = coefficients(model2f)[1] + coefficients(model2f)[3], 
              slope = coefficients(model2f)[2] + coefficients(model2f)[4], colour = f_colours[2])
  
hl <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_hl), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head length) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  geom_abline(intercept = coefficients(model3f)[1], 
              slope = coefficients(model3f)[2], colour = f_colours[1]) +
  geom_abline(intercept = coefficients(model3f)[1] + coefficients(model3f)[3], 
              slope = coefficients(model3f)[2] + coefficients(model3f)[4], colour = f_colours[2])
  
hh <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_hh), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head height) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))  +
  geom_abline(intercept = coefficients(model4f)[1], 
              slope = coefficients(model4f)[2], colour = f_colours[1]) +
  geom_abline(intercept = coefficients(model4f)[1] + coefficients(model4f)[3], 
              slope = coefficients(model4f)[2] + coefficients(model4f)[4], colour = f_colours[2])

(svl + hw) / (hl + hh)

# Save plot
#ggsave(here("figures/bodysize-bite-force-fossorial.png"), height = 5)
```

## Remove slopes...

Plots coloured by DIET

```{r}
# Remove NAs
lepidosaur_d <- filter(lepidosaur$data, !is.na(Diet))

svl <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_svl), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(SVL) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 

hw <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_hw), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head width) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 
  
hl <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_hl), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head length) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 
  
hh <-
  ggplot(lepidosaur_d, aes(y = log(max_bf), x = log(max_hh), colour = Diet)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = d_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head height) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12)) 

(svl + hw) / (hl + hh)

# Save plot
#ggsave(here("figures/bodysize-bite-force-diet-noslope.png"), height = 5)
```

Plots coloured by ARBOREAL

```{r}
# Remove NAs
lepidosaur_a <- filter(lepidosaur$data, !is.na(arboreal))

svl <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_svl), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(SVL) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none")

hw <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_hw), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head width) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 
  
hl <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_hl), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head length) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 
  
hh <-
  ggplot(lepidosaur_a, aes(y = log(max_bf), x = log(max_hh), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = a_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head height) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12))  

(svl + hw) / (hl + hh)

# Save plot
#ggsave(here("figures/bodysize-bite-force-arboreal-noslope.png"), height = 5)
```

Plots coloured by ARBOREAL

```{r}
# Remove NAs
lepidosaur_f <- filter(lepidosaur$data, !is.na(fossorial))

svl <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_svl), colour = fossorial)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(SVL) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "A") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 

hw <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_hw), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head width) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "B") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 
  
hl <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_hl), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head length) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "C") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12),
        legend.position = "none") 
  
hh <-
  ggplot(lepidosaur_f, aes(y = log(max_bf), x = log(max_hh), colour = arboreal)) + 
  geom_point(alpha = 0.5) +
  scale_colour_manual(values = f_colours) +
  theme_bw(base_size = 14) +
  xlab("ln(head height) (mm)") +
  ylab("ln(bite-force) (N)") + 
  #ylim(-3, 6) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(tag = "D") +
  theme(plot.tag = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 12)) 

(svl + hw) / (hl + hh)

# Save plot
#ggsave(here("figures/bodysize-bite-force-fossorial-noslope.png"), height = 5)
```